Translation of B Implementations to the LLVM: Control and Modularity

### 2013-09-07 translation.tex
Added to translation.tex a reminder to fix generation of initialization function (call to initialization of imported modules). Added B source exerpts for example07. Added B and Python data structure for example08 (multiple imports, with prefix, and state variables).

Initialization is done is two steps: first all imported modules are initialized,
second the initialization clause is executed.
\begin{align*}
  \trad{i}{Init} \isdef
  & \llvm{"define void @\PH{\B{i.id}}\$init\$() \{ \nl"} \\
  & \quad\llvm{\PH{\trad{i.impl}{\ListOf{InitImp}}}} \\
  & \quad\llvm{\PH{\trad{i.init, "exit"}{\ListOf{\B{Inst}}}_L}} \\
  & \quad\llvm{exit: ret void \nl} \\
  & \llvm{\}"}
\end{align*}
The initialization of an imported module is performed by a call to the
corresponding initialization function:
\begin{align*}
  \lefteqn{\trad{m}{InitImp} \isdef } \\
  & \LET \ell = \lbl \IN \\
  & \quad \llvm{"\PH{\ell} = getelementptr \PH{\state(\B{m.root})}* \%self\$, i32 0, i32 \PH{\idx(\B{m})}\nl}\\
  & \quad \llvm{call void @\PH{\B{m.id}}\$init\$(\PH{\state(\B{m})}*
    \PH{\ell})"}
\end{align*}

>>>>

Initialization is done is two steps: first all imported modules are
initialized,\DD{Verify that Python implementation includes call to such
  initialisation functions.}  second the initialization clause is executed.
\begin{align*}
  \trad{i}{Init} \isdef
  & \llvm{"define void @\PH{\B{i.id}}\$init\$() \{ \nl"} \\
  & \quad\llvm{\PH{\trad{i.impl}{\ListOf{InitImp}}}} \\
  & \quad\llvm{\PH{\trad{i.init, "exit"}{\ListOf{\B{Inst}}}_L}} \\
  & \quad\llvm{exit: ret void \nl} \\
  & \llvm{\}"}
\end{align*}
The initialization of an imported module is performed by a call to the
corresponding initialization function:
\begin{align*}
  \lefteqn{\trad{m}{InitImp} \isdef } \\
  & \LET \ell = \lbl \IN \\
  & \quad \llvm{"\PH{\ell} = getelementptr \PH{\state(\B{m.root})}* \%self\$, i32 0, i32 \PH{\idx(\B{m})}\nl}\\
  & \quad \llvm{call void @\PH{\B{m.id}}\$init\$(\PH{\state(\B{m})}*
    \PH{\ell})"}
\end{align*}
